Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints\thanks{This research was supported by the Russian Science Foundation, project No. 16-11-10150.}

### 2020-04-04 2019/NUMTA_Barkalov/SoftComputing/article.tex
Fix mistakes in English in the answers to reviewer

\begin{equation}\label{R_glob_equal_R_loc}
	R_{glob}(i) = \left( \frac{1-\frac{\mu}{\mu_M r_M^{glob}}}{1-\frac{\mu}{\mu_M r_M^{loc}}} \right)^2 R_{loc}(i),
\end{equation}
wherein the maximum value of the equalization coefficient is 
\begin{equation}\label{new_rho}
\rho=\left(\frac{1-1/r_{M}^{glob}}{1-1/r_{M}^{loc}}\right)^2 
\end{equation}
in the case when $\mu = \mu_M$. %, where $\mu = |z_i-z_{i-1}|/\Delta_i$ and $\mu_M$ is from (\ref{current_lower_bounds}).
The use of the equalization coefficient equal to $\rho$ from (\ref{new_rho}) in all cases will correspond to equalizing the largest possible difference between the values of $R_{loc}(i)$ and $R_{glob}(i)$ and will contribute to a more local nature of the search when the difference between $R_{loc}(i)$ and $R_{glob}(i)$ is not the largest, i.e. when $\mu < \mu_M$.

@@

Based on the relations (\ref{R_glob_equal_R_loc}) and (\ref{new_rho}), one can formulate an \textit{index algorithm with dual estimate of the Lipschitz constants} (hereafter referred to as IA-DL).

@@

\textbf{Proof}. As long as $\bar{x}$ is a limit point, there should exist a sequence of trial numbers $q^1, q^2,...$ meeting the conditions
\[
\bar{x} \in [x_{t-1}, x_t], \; x^{k+1} \in [x_{t-1}, x_t], \; t=t(k), k=q^1, q^2, ...,
\]
meaning that the interval $[x_{t-1}, x_t]$ containing the limit point $\bar{x}$ at the step $k$ is hit by the trial at the subsequent step $k+1$.

From Step 3 and Step 7 of the index algorithm follows that
\begin{equation}\label{max_gamma}
\max \{x_t-x^{k+1},x^{k+1}-x_{t-1}\} \leq \gamma (x_t-x_{t-1}),
\end{equation}
where $\gamma = \frac{r+1}{2r}<1$  and $ r=\min\{r_\nu:1\leq\nu\leq m+1\}>1$.
The contraction property (\ref{lim_delta_t}) and the property (\ref{nested_int}) for the product of all intervals (\ref{intervals_t}) are the consequences of (\ref{max_gamma}).

As shown in Lemma 1, at each iteration there exists an interval with strictly positive characteristic. Due to the rule (\ref{MaxR}) this leads to the conclusion that
intervals from (\ref{intervals_t}) should also have positive characteristics because they are hit by subsequent trials; i.e., the conditions (\ref{R_g_zero}) are necessary.

For intervals with indexes $\nu(x_{i-1}) = \nu(x_{i}) = \nu$ from the second condition of Theorem \ref{theorem:1} and (\ref{K_leq_L}) follows that
\[
\frac{\left|z_i-z_{i-1}\right|}{\Delta_i}\leq 2L_\nu\sqrt{N+3},
\]
and in accordance with (\ref{z_estimates}) the inequalities 
\[
z_i = g_\nu(y(x_i))\geq z_\nu^*, \; \nu=\nu(x_i)
\]
holds. Then from the rules (\ref{R_1})--(\ref{R_3}) it follows that $R(i) \leq 2\Delta_i$, if $\nu(x_{i-1}) \neq \nu(x_{i})$, and
\[
R(i) \leq \Delta_i\left(1+\left(\frac{2L_\nu\sqrt{N+3}}{r_\nu\mu_\nu}\right)^2\right), 
\]
if $\nu(x_{i-1}) = \nu(x_{i}) = \nu$. These inequalities combined with (\ref{lim_delta_t}) lead us to the validity of (\ref{lim_R}).

The lemma is proved.
}

@@

	Therefore, for large enough $k$, the following inequality will be true
\begin{equation}
	R_{glob}(j) > \rho R_{loc}(t).
\end{equation}
{\color{blue}
Indeed, both $j$ and $t$ depend from $k$, as the numbering of the trial points (by the lower index) changes at every iteration and the numbering of the intervals changes respectively.
%new text begin
However, $R_{glob}(j(k))>0$ is fixed for each $k \geq \bar k$ because $j(k)$ corresponds to the same interval for $k \geq \bar k$, whereas number $t(k)$ corresponds to different intervals with different characteristics $R_{loc}(t(k)) \rightarrow 0$. From this we can conclude that the condition $R_{glob}(j) > \rho R_{loc}(t)$ is fulfilled for a large enough value of $k$.
%new text end
}

>>>>

\begin{equation}\label{R_glob_equal_R_loc}
	R_{glob}(i) = \left( \frac{1-\frac{\mu}{\mu_M r_M^{glob}}}{1-\frac{\mu}{\mu_M r_M^{loc}}} \right)^2 R_{loc}(i),
\end{equation}
where the maximum value of the equalization coefficient is 
\begin{equation}\label{new_rho}
\rho=\left(\frac{1-1/r_{M}^{glob}}{1-1/r_{M}^{loc}}\right)^2 
\end{equation}
in the case when $\mu = \mu_M$. %, where $\mu = |z_i-z_{i-1}|/\Delta_i$ and $\mu_M$ is from (\ref{current_lower_bounds}).
The use of the equalization coefficient equal to $\rho$ from (\ref{new_rho}) in all cases will correspond to equalizing the largest possible difference between the values of $R_{loc}(i)$ and $R_{glob}(i)$ and will contribute to a more local nature of the search when the difference between $R_{loc}(i)$ and $R_{glob}(i)$ is not at its maximum, i.e. when $\mu < \mu_M$.

@@

Based on the relations (\ref{R_glob_equal_R_loc}) and (\ref{new_rho}), one can formulate an \textit{index algorithm with a dual estimate of the Lipschitz constants} (hereafter referred to as IA-DL).

@@

\textbf{Proof}. As long as $\bar{x}$ is a limit point, there should exist a sequence of trial numbers $q^1, q^2,...$ meeting the conditions
\[
\bar{x} \in [x_{t-1}, x_t], \; x^{k+1} \in [x_{t-1}, x_t], \; t=t(k), k=q^1, q^2, ...,
\]
meaning that the interval $[x_{t-1}, x_t]$ containing the limit point $\bar{x}$ at the step $k$ is hit in the trial at the subsequent step $k+1$.

From Step 3 and Step 7 of the index algorithm, it follows that
\begin{equation}\label{max_gamma}
\max \{x_t-x^{k+1},x^{k+1}-x_{t-1}\} \leq \gamma (x_t-x_{t-1}),
\end{equation}
where $\gamma = \frac{r+1}{2r}<1$  and $ r=\min\{r_\nu:1\leq\nu\leq m+1\}>1$.
The contraction property (\ref{lim_delta_t}) and the property (\ref{nested_int}) for the product of all intervals (\ref{intervals_t}) are the consequences of (\ref{max_gamma}).

As shown in Lemma 1, at each iteration there exists an interval with a strictly positive characteristic. Due to the rule (\ref{MaxR}) this leads to the conclusion that
intervals from (\ref{intervals_t}) should also have positive characteristics because they are hit by subsequent trials; i.e., the conditions (\ref{R_g_zero}) are necessary.

For intervals with indexes $\nu(x_{i-1}) = \nu(x_{i}) = \nu$, it follows from (\ref{current_lower_bounds}) that
\[
\frac{\left|z_i-z_{i-1}\right|}{\Delta_i}\leq \mu_\nu,
\]
and in accordance with (\ref{z_estimates}) the inequalities 
\[
z_i = g_\nu(y(x_i))\geq z_\nu^*, \; \nu=\nu(x_i),
\]
hold. Then from the rules (\ref{R_1})--(\ref{R_3}) it follows that 
\[
R(i) \leq 2\Delta_i, \; \text{if } \; \nu(x_{i-1}) \neq \nu(x_{i}),
\]
\[
R(i) \leq \Delta_i\left(1+\frac{1}{r_\nu^2}\right), \; \text{if } \; \nu(x_{i-1}) = \nu(x_{i}) = \nu.
\]
These inequalities combined with (\ref{lim_delta_t}) lead us to the validity of (\ref{lim_R}).
The lemma is proved.
}

@@

	Therefore, for large enough $k$, the following inequality will be true
\begin{equation}
	R_{glob}(j) > \rho R_{loc}(t).
\end{equation}
{\color{blue}
Indeed, both $j$ and $t$ depend on $k$, as the numbering of the trial points (by the lower index) changes at every iteration and the numbering of the intervals changes respectively.
%new text begin
However, $R_{glob}(j(k))>0$ is fixed for each $k \geq \bar k$ because $j(k)$ corresponds to the same interval for $k \geq \bar k$, whereas the number $t(k)$ corresponds to different intervals with different characteristics $R_{loc}(t(k)) \rightarrow 0$. From this we can conclude that the condition $R_{glob}(j) > \rho R_{loc}(t)$ is fulfilled for a large enough value of $k$.
%new text end
}
